---
title: "Going Further with the parallel quicksort"
author: "Benjamin Cathelineau"
date: "26/11/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Modifying the shell script in order to acquire metadata about the condition when the experiment was started

As suggested, I added a lot of metadata, like the number of processes, the cpu and ram usage...

I looked on the internet to find a way to extract most of theses metadata.

```{sh}
cat scripts/run_benchmarking2.sh
```

## Modyfing the C program in order not to have to deal with perl
Now, the C program directly outputs a csv file, because I don't know Perl and I don't have time to learn it. The printing was changed.

```
  printf(", %lf ", diff);

```



## Customizing the linux scheduler settings in order to increase our test priorities

At the start of the shell script, I run this command: 

```
sudo renice --priority -19 --pid $BASHPID > /dev/null

```

This changes the scheduler setting so that our test is favored. See [the man page](https://linux.die.net/man/1/nice). In short a lower niceness is better for the process. A higher niceness is worse.




# Analysing the new data, with confidence intervals

```{r}
library(dplyr)
library(ggplot2)
library(Rmisc)
library(tidyverse)

df = read.csv("data/fedora_2021-12-01/measurements_14:37.csv") # load the data from the CSV
df
```
You can see that now there is a lot more metadata for each entry

## plot and confidence interval on the time
Here I plot the new data and get essentialy the same result as before. I have to do a wierd transformation because of the way the data is now.
```{r}
# https://www.datanovia.com/en/fr/blog/comment-creer-un-ggplot-contenant-plusieurs-lignes/
df2 <- df %>%
  dplyr::select(Size, TimeSeq, TimePar,TimeBuiltIn) %>%
  gather(key = "variable", value = "value", -Size)

p <- ggplot(df2, aes(x=Size, y = value, color = variable)) + geom_point() +geom_smooth()

print(p)

```


Then I try to compute the confidence interval on time for each size and for each algorithm. That's a lot of data.
```{r}
# Intended for a .95 confidence
MY_CI <- function(data){
  data_mean = mean(data)
  std_dev = sd(data)
  final_mult= std_dev/length(data)
  return(c(up= data_mean+(final_mult*2),mean=data_mean,down= data_mean-(final_mult*2)))

}

df %>% group_by(Size) %>% group_map(~ CI(x=.x$TimeSeq,ci=.95))
df %>% group_by(Size) %>% group_map(~ MY_CI(.x$TimeSeq))
df %>% group_by(Size) %>% group_map(~ CI(x=.x$TimePar,ci=.95))
df %>% group_by(Size) %>% group_map(~ MY_CI(.x$TimePar))
df %>% group_by(Size) %>% group_map(~ CI(x=.x$TimeBuiltIn,ci=.95))
df %>% group_by(Size) %>% group_map(~ MY_CI(.x$TimeBuiltIn))
```


As you can see, I was not able to reproduce the behavior of the `CI` function from the `Rmisc`package. I found the source code for the `CI` function [here](https://rdrr.io/cran/Rmisc/src/R/CI.R), and I don't understand what they are doing with the `qt` function. Maybe it's related to what *Arnaud Legrand* said about the sample variance being unreliable.
However I'm pretty close to the same confidence interval nonetheless.

## Exploiting the metadata
I only had time to look at the temperature.
```{r}
df %>% ggplot(aes(x=Size, y=TEMPERATURE)) + geom_point()
```
I believe that what we see here is the first runs of the test slowly increasing the temperature, and then it mostly stagnates around 80-90c°.

In general, all the metadata should be able to tell us if something goes wrong.

# Using the profiler to figure out in what function most of the code spends its time

I added a new entry in the makefile to compile with the right option in order to use the `gprof` profiler

```{sh}
cat src/Makefile
```

```{sh}
make -C src/ clean
make -C src/ profiling
```
```{sh}
cat src/gprof.txt
```
We see that most of the time is spent in the `partition` function.
